Implementation and Evaluation of Routing Algorithm in GENI Software-Defined Networking

### 2018-06-06 paper.tex
update openvswitch

>>>>

     \qquad Open vSwitch is a open source, multi layer virtual switch implemented in software. It can be intergrated with hardware where it can act as as control plane. One example is it can handle OnpenFlow control plane in a hardware silicon. There are three mainly components in Open vSwitch: (a) Control Plane; (b) Kernel Mode; (c) Command line interface. 
